### 2014-07-22 MS.tex
sanchez

\section*{References}

1. Mitter C, Farrell B, Wiegmann B (1988) The phylogenetic study of
adaptive zones: has phytophagy promoted insect diversification? Am Nat
132: 107--128.
doi:\href{http://dx.doi.org/10.1086/284840}{10.1086/284840}.

2. Nyman T, Linder HP, Peña C, Malm T, Wahlberg N (2012) Climate-driven
diversity dynamics in plants and plant-feeding insects. Ecol Lett 15:
889--898. Available:
\url{http://doi.wiley.com/10.1111/j.1461-0248.2012.01782.x}. Accessed 29
March 2013.

3. Ehrlich PR, Raven PH (1964) Butterflies and plants: a study in
coevolution. Evolution 18: 586--608.

4. Janz N (2011) Ehrlich and raven revisited: mechanisms underlying
codiversification of plants and enemies. Annu Rev Ecol Evol S 42:
71--89. Available:
\url{http://www.annualreviews.org/doi/abs/10.1146/annurev-ecolsys-102710-145024}.

5. Nylin S, Slove J, Janz N (2013) Host plant utilization, host range
oscillations and diversification in nymphalid butterflies: a
phylogenetic investigation. Evolution: in press.

6. Nieukerken EJ van, Kaila L, Kitching IJ, Kristensen NP, Lees DC, et
al. (2011) Order lepidoptera. In:. Animal biodiversity: an outline of
higher-level classification and survey of taxonomic richness. Zootaxa.
pp. 212--221.

7. Heikkilä M, Kaila L, Mutanen M, Peña C, Wahlberg N (2012) Cretaceous
origin and repeated tertiary diversification of the redefined
butterflies. P Roy Soc B 279: 1093--1099. Available:
\href{http://rspb.royalsocietypublishing.org/cgi/doi/10.1098/rspb.2011.1430 http://www.ncbi.nlm.nih.gov/pubmed/21920981}{http://rspb.royalsocietypublishing.org/cgi/doi/10.1098/rspb.2011.1430
http://www.ncbi.nlm.nih.gov/pubmed/21920981}.

8. Elias M, Joron M, Willmott KR, Silva-Brandão KL, Kaiser V, et al.
(2009) Out of the andes: patterns of diversification in clearwing
butterflies. Mol Ecol 18: 1716--1729. Available:
\url{http://www.ncbi.nlm.nih.gov/pubmed/19386035}.

9. Fordyce JA (2010) Host shifts and evolutionary radiations of
butterflies. P Roy Soc B 277: 3735--3743. Available:
\url{http://www.pubmedcentral.nih.gov/articlerender.fcgi?artid=2992698\&tool=pmcentrez\&rendertype=abstract}.

10. Wahlberg N, Leneveu J, Kodandaramaiah U, Peña C, Nylin S, et al.
(2009) Nymphalid butterflies diversify following near demise at the
Cretaceous/Tertiary boundary. P Roy Soc B 276: 4295--4302. Available:
\url{http://rspb.royalsocietypublishing.org/cgi/doi/10.1098/rspb.2009.1303}.
Accessed 29 March 2013.

11. Peña C, Wahlberg N (2008) Prehistorical climate change increased
diversification of a group of butterflies. Biol Lett 4: 274--278.
Available:
\url{http://rsbl.royalsocietypublishing.org/cgi/doi/10.1098/rsbl.2008.0062}.
Accessed 29 March 2013.

12. Ferrer-Paris JR, Sánchez-Mercado A, Viloria ÁL, Donaldson J (2013)
Congruence and diversity of butterfly-host plant associations at higher
taxonomic levels. PloS one 8: e63570.

13. Alfaro ME, Santini F, Brock C, Alamillo H, Dornburg A, et al. (2009)
Nine exceptional radiations plus high turnover explain species diversity
in jawed vertebrates. P Natl Acad Sci USA 106: 13410--13414. Available:
\url{http://www.pubmedcentral.nih.gov/articlerender.fcgi?artid=2715324\$/backslash\$\&tool=pmcentrez\$/backslash\$\&rendertype=abstract}.

14. Harmon LJ, Rabosky DL, FitzJohn RG, Brown JW (2011) turboMEDUSA:
MEDUSA: modeling evolutionary diversification using stepwise AIC.

15. FitzJohn RG (2012) Diversitree: comparative phylogenetic analyses of
diversification in r. Method Ecol Evol 3: 1084--1092. Available:
\url{http://doi.wiley.com/10.1111/j.2041-210X.2012.00234.x}.

16. Lamas G (2004) Checklist: part 4A. hesperioidea-papilionoidea.
Gainesville.

17. Matos-Maraví PF, Peña C, Willmott KR, Freitas AV, Wahlberg N (2013)
Systematics and evolutionary history of butterflies in the ``Taygetis
clade'' (nymphalidae: satyrinae: euptychiina): towards a better
understanding of neotropical biogeography. Mol Phylogenet Evol 66:
54--68. Available:
\url{http://linkinghub.elsevier.com/retrieve/pii/S1055790312003624}.
Accessed 29 March 2013.

18. Brower AVZ, Wahlberg N, Ogawa JR, Boppré M, Vane-Wright RI (2010)
Phylogenetic relationships among genera of danaine butterflies
(lepidoptera: nymphalidae) as implied by morphology and DNA sequences.
Syst Biodivers 8: 75--89.
doi:\href{http://dx.doi.org/10.1080/14772001003626814}{10.1080/14772001003626814}.

19. Kodandaramaiah U, Lees DC, Müller CJ, Torres E, Karanth KP, et al.
(2010) Phylogenetics and biogeography of a spectacular old world
radiation of butterflies: the subtribe mycalesina (lepidoptera:
nymphalidae: satyrini). BMC Evol Biol 10: 172. Available:
\url{http://www.pubmedcentral.nih.gov/articlerender.fcgi?artid=2898688\&tool=pmcentrez\&rendertype=abstract}.

20. Kodandaramaiah U, Peña C, Braby MF, Grund R, Müller CJ, et al.
(2010) Phylogenetics of coenonymphina (nymphalidae: satyrinae) and the
problem of rooting rapid radiations. Mol Phylogenet Evol 54: 386--394.
Available:
\url{http://linkinghub.elsevier.com/retrieve/pii/S1055790309003273}.
Accessed 29 March 2013.

21. Ortiz-Acevedo E, Willmott KR (2013) Molecular systematics of the
butterfly tribe preponini (nymphalidae: charaxinae). Syst Entomol:
no--o. Available: \url{http://doi.wiley.com/10.1111/syen.12008}.

22. De-Silva DL, Day JJ, Elias M, Willmott KR, Whinnett A, et al. (2010)
Molecular phylogenetics of the neotropical butterfly subtribe oleriina
(nymphalidae: danainae: ithomiini). Mol Phylogenet Evol 55: 1032--1041.
Available: \url{http://www.ncbi.nlm.nih.gov/pubmed/20079859}.

23. Freitas AVL, Brown Jr. KS (2004) Phylogeny of the nymphalidae
(lepidoptera). Syst Biol 53: 363--383. Available:
\url{http://sysbio.oxfordjournals.org/cgi/doi/10.1080/10635150490445670}.

24. Peña C, Wahlberg N, Weingartner E, Kodandaramaiah U, Nylin S, et al.
(2006) Higher level phylogeny of satyrinae butterflies (lepidoptera:
nymphalidae) based on DNA sequence data. Mol Phylogenet Evol 40: 29--49.
Available: \url{http://www.ncbi.nlm.nih.gov/pubmed/16563805}.

25. Penz CM (1999) Higher level phylogeny for the passion-vine
butterflies (nymphalidae, heliconiinae) based on early stage and adult
morphology. Zool J Linn Soc 127: 277--344. Available:
\url{http://doi.wiley.com/10.1111/j.1096-3642.1999.tb00680.x}. Accessed
03 September 2013.

26. Silva-Brandão KL, Wahlberg N, Francini RB, Azeredo-Espin AML, Brown
Jr. KS, et al. (2008) Phylogenetic relationships of butterflies of the
tribe acraeini (lepidoptera, nymphalidae, heliconiinae) and the
evolution of host plant use. Mol Phylogenet Evol 46: 515--531.
Available: \url{http://www.ncbi.nlm.nih.gov/pubmed/18191590}.

27. Peña C, Nylin S, Wahlberg N (2011) The radiation of satyrini
butterflies (nymphalidae: satyrinae): a challenge for phylogenetic
methods. Zool J Linn Soc 161: 64--87. Available:
\url{http://doi.wiley.com/10.1111/j.1096-3642.2009.00627.x}. Accessed 29
March 2013.

28. Peña C, Nylin S, Freitas AVL, Wahlberg N (2010) Biogeographic
history of the butterfly subtribe euptychiina (lepidoptera, nymphalidae,
satyrinae). Zool Scr 39: 243--258. Available:
\url{http://blackwell-synergy.com/doi/abs/10.1111/j.1463-6409.2010.00421.x}.

29. Ackery PR (1988) Hostplants and classification: a review of
nymphalid butterflies. Biol J Linn Soc 33: 95--203.

@@

31. Beccaloni G, Viloria Á, Hall S, Robinson G (2008) Catalogue of the
hostplants of the neotropical butterflies. London: The Natural History
Museum.

32. Janzen DH, Hallwachs W (2009) Dynamic database for an inventory of
the macrocaterpillar fauna, and its food plants and parasitoids, of area
de conservacion guanacaste (aCG), northwestern costa rica. Available:
\url{http://janzen.sas.upenn.edu}. Accessed 17 April 2013.

33. Core Team R (2013) R: a language and environment for statistical
computing. Vienna, Austria: R Foundation for Statistical Computing.
Available: \url{http://www.r-project.org}.

34. Popescu A-A, Huber KT, Paradis E (2012) ape 3.0: new tools for
distance-based phylogenetics and evolutionary analysis in r.
Bioinformatics 28: 1536--1537.

35. Harmon LJ, Weir JT, Brock CD, Glor RE, Challenger W (2008) GEIGER:
investigating evolutionary radiations. Bioinformatics 24: 129--131.
Available: \url{http://www.ncbi.nlm.nih.gov/pubmed/18006550}.

36. Maddison WP, Midford PE, Otto SP (2007) Estimating a binary
character's effect on speciation and extinction. Syst Biol 56: 701--710.
Available: \url{http://www.ncbi.nlm.nih.gov/pubmed/17849325}.

37. Willmott KR, Freitas AVL (2006) Higher-level phylogeny of the
ithomiinae (lepidoptera: nymphalidae): classification, patterns of
larval hostplant colonization and diversification. Cladistics 22:
297--368. Available:
\url{http://doi.wiley.com/10.1111/j.1096-0031.2006.00108.x}.

38. Scott JA (1986) The butterflies of north america. Stanford
University Press.

39. Davis MP, Midford PE, Maddison W (2013) Exploring power and
parameter estimation of the BiSSE method for analyzing species
diversification. BMC Evol Biol 13: 38. Available:
\url{http://www.biomedcentral.com/1471-2148/13/38}.

40. Litman JR, Danforth BN, Eardley CD, Praz CJ (2011) Why do leafcutter
bees cut leaves? new insights into the early evolution of bees. P Roy
Soc B 278: 3593--3600. Available:
\url{http://www.pubmedcentral.nih.gov/articlerender.fcgi?artid=3189370\$/backslash\$\&tool=pmcentrez\$/backslash\$\&rendertype=abstract}.

41. Ryberg M, Matheny PB (2012) Asynchronous origins of ectomycorrhizal
clades of agaricales. P Roy Soc B 279: 2003--2011. Available:
\url{http://www.ncbi.nlm.nih.gov/pubmed/22171078}.

42. Brown Jr. KS (1987) Chemistry at the Solanaceae/Ithomiinae
interface. Ann Mo Bot Gard 74: 359--397.

43. Brower AVZ, Freitas AVL, Lee M-M, Silva-Brandão KL, Whinnett A, et
al. (2006) Phylogenetic relationships among the ithomiini (lepidoptera:
nymphalidae) inferred from one mitochondrial and two nuclear gene
regions. Syst Entomol 31: 288--301. Available:
\url{http://doi.wiley.com/10.1111/j.1365-3113.2006.00321.x}.

@@

46. Li W, Schuler MA, Berenbaum MR (2003) Diversification of
furanocoumarin-metabolizing cytochrome p450 monooxygenases in two
papilionids: specificity and substrate encounter rate. P Natl Acad Sci
USA 100: 14593--14598. Available:
\url{http://www.pnas.org/content/100/suppl.2/14593.abstract}.

47. Bell CD, Soltis DE, Soltis PS (2010) The age and diversification of
the angiosperms re-revisited. Am J Bot 97: 1296--1303. Available:
\url{http://www.ncbi.nlm.nih.gov/pubmed/21616882}.

48. Somoza R (1998) Updated nazca (farallon) - south america relative
motions during the last 40 my: implications for mountain building in the
central andean region. J S Am Earth Sci 11: 211--215.

49. Hoorn C, Wesselingh FP, Steege H ter, Bermudez MA, Mora A, et al.
(2010) Amazonia through time: andean uplift, climate change, landscape
evolution, and biodiversity. Science 330: 927--931. Available:
\url{http://www.ncbi.nlm.nih.gov/pubmed/21071659}.

50. Olmstead RG (2013) Phylogeny and biogeography in solanaceae,
verbenaceae and bignoniaceae: a comparison of continental and
intercontinental diversification patterns. Bot J Linn Soc 171: 80--102.
Available: \url{http://doi.wiley.com/10.1111/j.1095-8339.2012.01306.x}.

51. Wahlberg N, Rubinoff D (2011) Vagility across vanessa (lepidoptera:
nymphalidae): mobility in butterfly species does not inhibit the
formation and persistence of isolated sister taxa. Syst Entomol 36:
362--370. Available:
\url{http://doi.wiley.com/10.1111/j.1365-3113.2010.00566.x}. Accessed 16
April 2013.

52. Müller CJ, Wahlberg N, Beheregaray LB (2010) `After africa': the
evolutionary history and systematics of the genus charaxes ochsenheimer
(lepidoptera: nymphalidae) in the indo-pacific region. Biol J Linn Soc
100: 457--481. Available:
\url{http://doi.wiley.com/10.1111/j.1095-8312.2010.01426.x}.

53. Aduse-Poku K, Vingerhoedt E, Wahlberg N (2009) Out-of-africa again:
a phylogenetic hypothesis of the genus charaxes (lepidoptera:
nymphalidae) based on 5 gene regions. Mol Phylogenet Evol 53: 463--478.
doi:\href{http://dx.doi.org/10.1016/j.ympev.2009.06.021}{10.1016/j.ympev.2009.06.021}.

>>>>

\section*{References}
1. Mitter C, Farrell B, Wiegmann B (1988) The phylogenetic study of
adaptive zones: has phytophagy promoted insect diversification? Am Nat
132: 107--128.
doi:\href{http://dx.doi.org/10.1086/284840}{10.1086/284840}.

2. Nyman T, Linder HP, Peña C, Malm T, Wahlberg N (2012) Climate-driven
diversity dynamics in plants and plant-feeding insects. Ecol Lett 15:
889--898.
doi:\href{http://dx.doi.org/10.1111/j.1461-0248.2012.01782.x}{10.1111/j.1461-0248.2012.01782.x}.

3. Ehrlich PR, Raven PH (1964) Butterflies and plants: A study in
coevolution. Evolution 18: 586--608.
doi:\href{http://dx.doi.org/10.2307/2406212}{10.2307/2406212}.

4. Janz N (2011) Ehrlich and Raven Revisited: Mechanisms Underlying
Codiversification of Plants and Enemies. Annu Rev Ecol Evol S 42:
71--89.
doi:\href{http://dx.doi.org/10.1146/annurev-ecolsys-102710-145024}{10.1146/annurev-ecolsys-102710-145024}.

5. Nylin S, Slove J, Janz N (2014) Host plant utilization, host range
oscillations and diversification in Nymphalid butterflies: A
phylogenetic investigation. Evolution 68: 105--124.
doi:\href{http://dx.doi.org/10.1111/evo.12227}{10.1111/evo.12227}.

6. Nieukerken EJ van, Kaila L, Kitching IJ, Kristensen NP, Lees DC, et
al. (2011) Order Lepidoptera. In:. Animal biodiversity: an outline of
higher-level classification and survey of taxonomic richness. Zootaxa.
pp. 212--221.

7. Heikkilä M, Kaila L, Mutanen M, Peña C, Wahlberg N (2012) Cretaceous
origin and repeated tertiary diversification of the redefined
butterflies. P Roy Soc B 279: 1093--1099.
doi:\href{http://dx.doi.org/10.1098/rspb.2011.1430}{10.1098/rspb.2011.1430}.

8. Elias M, Joron M, Willmott KR, Silva-Brandão KL, Kaiser V, et al.
(2009) Out of the Andes: Patterns of diversification in clearwing
butterflies. Mol Ecol 18: 1716--1729.
doi:\href{http://dx.doi.org/10.1111/j.1365-294X.2009.04149.x}{10.1111/j.1365-294X.2009.04149.x}.

9. Fordyce JA (2010) Host shifts and evolutionary radiations of
butterflies. P Roy Soc B 277: 3735--3743.
doi:\href{http://dx.doi.org/10.1098/rspb.2010.0211}{10.1098/rspb.2010.0211}.

10. Wahlberg N, Leneveu J, Kodandaramaiah U, Peña C, Nylin S, et al.
(2009) Nymphalid butterflies diversify following near demise at the
Cretaceous/Tertiary boundary. P Roy Soc B 276: 4295--4302.
doi:\href{http://dx.doi.org/10.1098/rspb.2009.1303}{10.1098/rspb.2009.1303}.

11. Peña C, Wahlberg N (2008) Prehistorical climate change increased
diversification of a group of butterflies. Biol Lett 4: 274--278.
doi:\href{http://dx.doi.org/10.1098/rsbl.2008.0062}{10.1098/rsbl.2008.0062}.

12. Ferrer-Paris JR, S\'anchez-Mercado A, Viloria ÁL, Donaldson J (2013)
Congruence and Diversity of Butterfly-Host Plant Associations at Higher
Taxonomic Levels. PloS one 8: e63570.
doi:\href{http://dx.doi.org/0.1371/journal.pone.0063570}{0.1371/journal.pone.0063570}.

13. Alfaro ME, Santini F, Brock C, Alamillo H, Dornburg A, et al. (2009)
Nine exceptional radiations plus high turnover explain species diversity
in jawed vertebrates. P Natl Acad Sci USA 106: 13410--13414.
doi:\href{http://dx.doi.org/10.1073/pnas.0811087106}{10.1073/pnas.0811087106}.

14. Harmon LJ, Rabosky DL, FitzJohn RG, Brown JW (2011) turboMEDUSA:
MEDUSA: Modeling Evolutionary Diversification Using Stepwise AIC.

15. FitzJohn RG (2012) Diversitree: comparative phylogenetic analyses of
diversification in R. Method Ecol Evol 3: 1084--1092.
doi:\href{http://dx.doi.org/10.1111/j.2041-210X.2012.00234.x}{10.1111/j.2041-210X.2012.00234.x}.

16. Lamas G (2004) Checklist: Part 4A. Hesperioidea-Papilionoidea.
Gainesville.

17. Matos-Maraví PF, Peña C, Willmott KR, Freitas AV, Wahlberg N (2013)
Systematics and evolutionary history of butterflies in the ``Taygetis
clade'' (Nymphalidae: Satyrinae: Euptychiina): Towards a better
understanding of Neotropical biogeography. Mol Phylogenet Evol 66:
54--68.
doi:\href{http://dx.doi.org/10.1016/j.ympev.2012.09.005}{10.1016/j.ympev.2012.09.005}.

18. Brower AVZ, Wahlberg N, Ogawa JR, Boppré M, Vane-Wright RI (2010)
Phylogenetic relationships among genera of danaine butterflies
(Lepidoptera: Nymphalidae) as implied by morphology and DNA sequences.
Syst Biodivers 8: 75--89.
doi:\href{http://dx.doi.org/10.1080/14772001003626814}{10.1080/14772001003626814}.

19. Kodandaramaiah U, Lees DC, Müller CJ, Torres E, Karanth KP, et al.
(2010) Phylogenetics and biogeography of a spectacular Old World
radiation of butterflies: the subtribe Mycalesina (Lepidoptera:
Nymphalidae: Satyrini). BMC Evol Biol 10: 172. Available:
\url{http://www.pubmedcentral.nih.gov/articlerender.fcgi?artid=2898688\&tool=pmcentrez\&rendertype=abstract}.

20. Kodandaramaiah U, Peña C, Braby MF, Grund R, Müller CJ, et al.
(2010) Phylogenetics of Coenonymphina (Nymphalidae: Satyrinae) and the
problem of rooting rapid radiations. Mol Phylogenet Evol 54: 386--394.
doi:\href{http://dx.doi.org/10.1016/j.ympev.2009.08.012}{10.1016/j.ympev.2009.08.012}.

21. Ortiz-Acevedo E, Willmott KR (2013) Molecular systematics of the
butterfly tribe Preponini (Nymphalidae: Charaxinae). Syst Entomol:
no--o.
doi:\href{http://dx.doi.org/10.1111/syen.12008}{10.1111/syen.12008}.

22. De-Silva DL, Day JJ, Elias M, Willmott KR, Whinnett A, et al. (2010)
Molecular phylogenetics of the Neotropical butterfly subtribe Oleriina
(Nymphalidae: Danainae: Ithomiini). Mol Phylogenet Evol 55: 1032--1041.
doi:\href{http://dx.doi.org/http://dx.doi.org/10.1016/j.ympev.2010.01.010}{http://dx.doi.org/10.1016/j.ympev.2010.01.010}.

23. Freitas AVL, Brown Jr. KS (2004) Phylogeny of the Nymphalidae
(Lepidoptera). Syst Biol 53: 363--383.
doi:\href{http://dx.doi.org/10.1080/10635150490445670}{10.1080/10635150490445670}.

24. Peña C, Wahlberg N, Weingartner E, Kodandaramaiah U, Nylin S, et al.
(2006) Higher level phylogeny of Satyrinae butterflies (Lepidoptera:
Nymphalidae) based on DNA sequence data. Mol Phylogenet Evol 40: 29--49.
doi:\href{http://dx.doi.org/10.1016/j.ympev.2006.02.007}{10.1016/j.ympev.2006.02.007}.

25. Penz CM (1999) Higher level phylogeny for the passion-vine
butterflies (Nymphalidae, Heliconiinae) based on early stage and adult
morphology. Zool J Linn Soc 127: 277--344.
doi:\href{http://dx.doi.org/10.1111/j.1096-3642.1999.tb00680.x}{10.1111/j.1096-3642.1999.tb00680.x}.

26. Silva-Brandão KL, Wahlberg N, Francini RB, Azeredo-Espin AML, Brown
Jr. KS, et al. (2008) Phylogenetic relationships of butterflies of the
tribe Acraeini (Lepidoptera, Nymphalidae, Heliconiinae) and the
evolution of host plant use. Mol Phylogenet Evol 46: 515--531.
doi:\href{http://dx.doi.org/10.1016/j.ympev.2007.11.024}{10.1016/j.ympev.2007.11.024}.

27. Peña C, Nylin S, Wahlberg N (2011) The radiation of Satyrini
butterflies (Nymphalidae: Satyrinae): a challenge for phylogenetic
methods. Zool J Linn Soc 161: 64--87.
doi:\href{http://dx.doi.org/10.1111/j.1096-3642.2009.00627.x}{10.1111/j.1096-3642.2009.00627.x}.

28. Peña C, Nylin S, Freitas AVL, Wahlberg N (2010) Biogeographic
history of the butterfly subtribe Euptychiina (Lepidoptera, Nymphalidae,
Satyrinae). Zool Scr 39: 243--258.
doi:\href{http://dx.doi.org/10.1111/j.1463-6409.2010.00421.x}{10.1111/j.1463-6409.2010.00421.x}.

29. Ackery PR (1988) Hostplants and classification: a review of
nymphalid butterflies. Biol J Linn Soc 33: 95--203.
doi:\href{http://dx.doi.org/10.1111/j.1095-8312.1988.tb00446.x}{10.1111/j.1095-8312.1988.tb00446.x}.

@@

31. Beccaloni G, Viloria Á, Hall S, Robinson G (2008) Catalogue of the
hostplants of the Neotropical butterflies. London: The Natural History
Museum.

32. Janzen DH, Hallwachs W (2009) Dynamic database for an inventory of
the macrocaterpillar fauna, and its food plants and parasitoids, of Area
de Conservacion Guanacaste (ACG), northwestern Costa Rica. Available:
\url{http://janzen.sas.upenn.edu}. Accessed 17 April 2013.

33. Core Team R (2013) R: A Language and Environment for Statistical
Computing. Vienna, Austria: R Foundation for Statistical Computing.
Available: \url{http://www.r-project.org}.

34. Popescu A-A, Huber KT, Paradis E (2012) ape 3.0: New tools for
distance-based phylogenetics and evolutionary analysis in R.
Bioinformatics 28: 1536--1537.
doi:\href{http://dx.doi.org/10.1093/bioinformatics/bts184}{10.1093/bioinformatics/bts184}.

35. Harmon LJ, Weir JT, Brock CD, Glor RE, Challenger W (2008) GEIGER:
investigating evolutionary radiations. Bioinformatics 24: 129--131.
doi:\href{http://dx.doi.org/10.1093/bioinformatics/btm538}{10.1093/bioinformatics/btm538}.

36. Maddison WP, Midford PE, Otto SP (2007) Estimating a binary
character's effect on speciation and extinction. Syst Biol 56: 701--710.
doi:\href{http://dx.doi.org/10.1080/10635150701607033}{10.1080/10635150701607033}.

37. Willmott KR, Freitas AVL (2006) Higher-level phylogeny of the
Ithomiinae (Lepidoptera: Nymphalidae): classification, patterns of
larval hostplant colonization and diversification. Cladistics 22:
297--368.
doi:\href{http://dx.doi.org/10.1111/j.1096-0031.2006.00108.x}{10.1111/j.1096-0031.2006.00108.x}.

38. Scott JA (1986) The Butterflies of North America. Stanford
University Press.

39. Davis MP, Midford PE, Maddison W (2013) Exploring power and
parameter estimation of the BiSSE method for analyzing species
diversification. BMC Evol Biol 13: 38.
doi:\href{http://dx.doi.org/10.1186/1471-2148-13-38}{10.1186/1471-2148-13-38}.

40. Litman JR, Danforth BN, Eardley CD, Praz CJ (2011) Why do leafcutter
bees cut leaves? New insights into the early evolution of bees. P Roy
Soc B 278: 3593--3600.
doi:\href{http://dx.doi.org/10.1098/rspb.2011.0365}{10.1098/rspb.2011.0365}.

41. Ryberg M, Matheny PB (2012) Asynchronous origins of ectomycorrhizal
clades of Agaricales. P Roy Soc B 279: 2003--2011.
doi:\href{http://dx.doi.org/10.1098/rspb.2011.2428}{10.1098/rspb.2011.2428}.

42. Brown Jr. KS (1987) Chemistry at the Solanaceae/Ithomiinae
Interface. Ann Mo Bot Gard 74: 359--397.

43. Brower AVZ, Freitas AVL, Lee M-M, Silva-Brandão KL, Whinnett A, et
al. (2006) Phylogenetic relationships among the Ithomiini (Lepidoptera:
Nymphalidae) inferred from one mitochondrial and two nuclear gene
regions. Syst Entomol 31: 288--301.
doi:\href{http://dx.doi.org/10.1111/j.1365-3113.2006.00321.x}{10.1111/j.1365-3113.2006.00321.x}.

@@

46. Li W, Schuler MA, Berenbaum MR (2003) Diversification of
furanocoumarin-metabolizing cytochrome P450 monooxygenases in two
papilionids: Specificity and substrate encounter rate. P Natl Acad Sci
USA 100: 14593--14598.
doi:\href{http://dx.doi.org/10.1073/pnas.1934643100}{10.1073/pnas.1934643100}.

47. Bell CD, Soltis DE, Soltis PS (2010) The age and diversification of
the angiosperms re-revisited. Am J Bot 97: 1296--1303.
doi:\href{http://dx.doi.org/10.3732/ajb.0900346}{10.3732/ajb.0900346}.

48. Somoza R (1998) Updated Nazca (Farallon) - South America relative
motions during the last 40 My: implications for mountain building in the
central Andean region. J S Am Earth Sci 11: 211--215.
doi:\href{http://dx.doi.org/10.1016/S0895-9811(98)00012-1}{10.1016/S0895-9811(98)00012-1}.

49. Hoorn C, Wesselingh FP, Steege H ter, Bermudez MA, Mora A, et al.
(2010) Amazonia through time: Andean uplift, climate change, landscape
evolution, and biodiversity. Science 330: 927--931.
doi:\href{http://dx.doi.org/10.1126/science.1194585}{10.1126/science.1194585}.

50. Olmstead RG (2013) Phylogeny and biogeography in Solanaceae,
Verbenaceae and Bignoniaceae: a comparison of continental and
intercontinental diversification patterns. Bot J Linn Soc 171: 80--102.
doi:\href{http://dx.doi.org/10.1111/j.1095-8339.2012.01306.x}{10.1111/j.1095-8339.2012.01306.x}.

51. Wahlberg N, Rubinoff D (2011) Vagility across Vanessa (Lepidoptera:
Nymphalidae): mobility in butterfly species does not inhibit the
formation and persistence of isolated sister taxa. Syst Entomol 36:
362--370.
doi:\href{http://dx.doi.org/10.1111/j.1365-3113.2010.00566.x}{10.1111/j.1365-3113.2010.00566.x}.

52. Müller CJ, Wahlberg N, Beheregaray LB (2010) `After Africa': the
evolutionary history and systematics of the genus Charaxes Ochsenheimer
(Lepidoptera: Nymphalidae) in the Indo-Pacific region. Biol J Linn Soc
100: 457--481.
doi:\href{http://dx.doi.org/10.1111/j.1095-8312.2010.01426.x}{10.1111/j.1095-8312.2010.01426.x}.

53. Aduse-Poku K, Vingerhoedt E, Wahlberg N (2009) Out-of-Africa again:
a phylogenetic hypothesis of the genus Charaxes (Lepidoptera:
Nymphalidae) based on 5 gene regions. Mol Phylogenet Evol 53: 463--478.
doi:\href{http://dx.doi.org/10.1016/j.ympev.2009.06.021}{10.1016/j.ympev.2009.06.021}.
